%
% LaTeX source for resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[letterpaper,margin=0.55in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\usepackage{enumitem}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Ajinkya Tupkar Jain}{}{}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:tupkarajinkya@gmail.com}{tupkarajinkya\mbox{}@\mbox{}gmail.com}\sbull +91-997-434-1333\sbull
%\\
%F1202, Mantri Celestia\sbull
Hyderabad\sbull TS 500081\sbull India
\sbull\href{https://github.com/ajinkyaTupkar}{GitHub}
\sbull\href{https://www.linkedin.com/in/ajinkya-tupkar-jain-a9b55157/}{LinkedIn}
\spacedhrule{0.5em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{}{Indian Institute of Technology Gandhinagar}}
  {\textsc{Gandhinagar, Gujarat, India}} {%
  \headedsubsection
    {Bachelor of Technology (B.Tech.)~in Electrical Engineering with Minor in Computer Science And Engineering, \textit{Percentage:~83.6\%}}
    {July~'12 -- May~'16} {}
}

\headedsection
{\href{}{St. Arnold's Hr. Sec. School}}
{\textsc{Indore, MP, India}} {%
  \headedsubsection
  {Senior Secondary (AISSCE, CBSE), \textit{Percentage:~91\%}}
  {April~'11} {}

  \headedsubsection
  {Secondary (AISSE, CBSE), \textit{Percentage:~92\%}}
  {April~'09} {}
  
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{}{\textbf{Lead Engineer}}}
  {\textbf{}}

  {%
  \headedsubsection
    {Arcesium India Pvt Ltd}
    {December~'21 -- Present}
    {\bodytext{
    \begin{itemize}
    \item As part of Forward Deployed Software Engineering within Arcesium, executed and delivered multiple long-term and short-term client solutions in a fast-paced environment to meet onboarding and expansion requirements of clients.
    \item Managed and led multiple high-performing teams ranging from 4-8 members to deliver complex, robust, and scalable solutions in an agile environment.
    \item As lead engineer, owned end-to-end execution of project including planning, solution design, execution, delivery, and maintenance of projects.
    \item Delivered AI agents using AWS Bedrock and LangGraph to assist in support activities, resulting in 50\% reduction in developer time spent on support activities.
    \item Designed and implemented centralized GitLab CI/CD templates to streamline deployment pipelines for the entire department. This also contributed to improved developer productivity by eliminating repeated efforts to create CI/CD pipelines for each new project.
    \item Designed and implemented optimized data pipelines for processing ~5 million records daily using python, spark, and delta lake.
    \item Received multiple recognitions for timely and quality delivery of time sensitive client projects.
    \item Tech stack includes \textbf{Python, Spark, AsyncIO, Argo, Kubernetes, LangGraph, AWS(Bedrock, SQS, SNS, S3, )}
    
    \end{itemize}
}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{}{\textbf{Senior Software Engineer}}}
  {\textbf{}}

  {%
  \headedsubsection
    {Deepen AI, Arcsine Software Pvt Ltd}
    {December~'18 -- November~'21}
    {\bodytext{
    \begin{itemize}
    \item Joined as 4th Software Engineer in this bootstrapped start up as part of the 5 member founding team. Worked on multiple software engineering dimensions to transition the product from 10 daily active users to 1k+ daily active users.
    \item Led an engineering team of 8 members to deliver the product road map as well as fluid and dynamic client requirements.
    \item Revamped the existing Angular web application to a robust and scalable one using React and Redux based frontend.  
\item Led all data ingestion activities including analyzing, validating and transforming the
incoming data from customers.
\item Owned the entire DevOps and Release cycle, including maintenance and configuration of entire cloud infrastructure for reliability and
scalability. Also, worked closely with QA team to ensure highest quality of deliveries.
\item Worked closely with Ops and Hiring team and provided my insights to create scalable and sustainable processes within admin, ops and hiring activities to support growth of the company.
\item Tech stack includes \textbf{ReactJs, Redux-Saga, Python, Django, Angular, Apache, Nginx, Docker, Kubernetes, Google
Cloud Platform.}
    \end{itemize}
}}
}


\headedsection  % sets the header for the section and includes any subsections
  {\href{}{\textbf{Software Engineer}}}
  {\textbf{}}

  {%
  \headedsubsection
    {Optum, A UnitedHealth Group Company}
    {July~'16 -- November~'18}
    {\bodytext{
    \begin{itemize}
    \item Handled end to end development for the product responsible for role based provisioning across the organization.
     \item Actively participated in transition of dev-ops activities from XL Deployments to Jenkins Pipelines. Worked with OpenShift deployments and ELK stack for Logging.
         
      \item Actively involved in the development of next generation UI for the product. Worked on Angular 4 for UI, Spring Boot for MicroServices and Zuul implementation for authorization gateway. 
      \item Performed regular testing and wrote automated tests for UI using Selenium framework. Worked on performance testing of APIs using JMeter and New Relic.
      \item Actively involved with end-to-end deployment activities till production of Angular UI.
      \item Received a performance award for Redis implementation.
    \end{itemize}
}}
}
  {%
  \headedsubsection
    {Federated Data Storage}
    {Jan~'18 -- June~'18}
    {\bodytext{
    \begin{itemize}
    \item Worked on product enhancements to accommodate customer requirements.
    \item Created apis and hook based workflows on the apis to trigger processes based on api calls.  
    \item Worked on a diverse tech stack including MongoDB, RabbitMQ, OpenOffice, MySQL.
    \item Received a performance award for timely delivery in a very tight deadline.
    \end{itemize}
}}
}
  {%
  \headedsubsection
    {Identity Matching Solutions}
    {June~'18 -- Present}
    {\bodytext{
    \begin{itemize}
    \item Working on migration of product from BDPaas to public cloud (AWS).
    \item Working on Big Data tech stack including Hadoop, Hbase, HDFS, Elastic Search, MapReduce, terraform and Kubernetes.
    \end{itemize}
}}
}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Selected Projects}
% \vspace{0.15cm}
%\begin{itemize}[leftmargin=*]

  {%
  \headedsubsection{Appointment Scheduler}
    {Optum Global Hackathon - 2017}
    {\bodytext{
    \begin{itemize}
    \item Used Machine Learning algorithms to predict No-show of a patient for an appointment.
    \item Used the prediction to overbook and schedule the appointments.
    \end{itemize}
}}
}
  {%
  \headedsubsection
    {Telemedicine Platform using Blockchain}
    {Optum Global Hackathon - 2018}
    {\bodytext{
    \begin{itemize}
    \item Developed a blockchain based telemedicine platform.
    \item Provided an option of 2nd opinion and deducted fee accordingly.
    \end{itemize}
}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Additional Activities}
\vspace{0.15cm}
\begin{itemize}[labelindent=1.5em,labelsep=-0.3cm,leftmargin=*]
\item \headedsubsection 
{\href{}{\normalfont Hackathon Enthusiast
}}{{{}}}
{\bodytext{Winner under Machine Learning category for Optum Global Hackathon 2017, participated in the 2018 hackathon.}}

\item \headedsubsection 
{{\normalfont Convener, Student Senate (IIT Gandhinagar, 2015-16)
}}{{{}}}
{\bodytext{Elected representative solely responsible for the day to day activities of the Student Senate.}}


\item \headedsubsection 
{{\normalfont Student Coordinator, Career Development Services (Placement Office)(IIT Gandhinagar, 2015-16)
}}{{{}}}
{\bodytext{Worked as a student coordinator to invite companies and institutes for internships and placements.}}
\end{itemize}

\end{document}